Evolution of the AGN UV luminosity function from redshift 7.5

### 2018-04-10 Paper/paper.tex
Update text

\begin{figure*}
  \begin{center}
    \begin{tabular}{cc}
      \includegraphics[width=0.47\textwidth]{emissivity_18.pdf} & 
      \includegraphics[width=0.47\textwidth]{emissivity_21.pdf} \\
      % gammapi.py -- draw_emissivity()
    \end{tabular}
  \end{center}
  \caption{The 912~\AA\ emissivity of AGN assuming 100\% escape
    fraction down to a limiting magnitude.  Brown points show the
    emissivity when the best-fit double power law luminosity functions
    at respective redshifts are integrated down to $M_{1450}=-18$.
    Black points show the integration limit when the limit is assumed
    to be $M_{1450}=-21$.  For comparison, various other published
    models of the 1~Ry emissivity of AGN are also shown.  The blue
    curve in these panels shows the AGN 912~\AA\ emissivity model of
    \citet{2012ApJ...746..125H}, which is very similar to the model of
    \citet{2007ApJ...654..731H}.  Red circles with error bars show the
    determination from the fits of \citet{2015AA...578A..83G}.  The
    maroon curve is the published fit to the 1~Ry emissivity evolution
    in the fits of \citet{2017MNRAS.466.1160M}.  The green curve is
    the model of \citet{2015ApJ...813L...8M}.  The grey and brown
    curves show the best-fit form of Equation XX. \gk{Mention MH15 and
      HM12 Lstar limits.  Mention that Akiyama open and filled circles
      are very close.}}
  \label{fig:e912_2}
\end{figure*}

@@

@@

We can now calculate the contribution of quasars to the hydrogen
photoionization rate in the intergalactic medium (IGM).  We assume
that all quasars have a universal UV SED, parameterised by
\citet{2015MNRAS.449.4204L} as a power law with a break at 912~{\AA},
\begin{equation}
f_\nu\propto\begin{cases}
               \nu^{-0.61\pm 0.01} & \text{if}~\lambda\geq 912~\text{\AA},\\
               \nu^{-1.70\pm 0.61} & \text{if}~600~\text{\AA}<\lambda<912~\text{\AA}.\\                
               \end{cases}
\label{eqn:sed}
\end{equation}
This fit was derived by \citet{2015MNRAS.449.4204L} from a composite
spectrum of 53 quasars at $z\sim 2.4$.

While four published composite quasar UV SEDs
\citep{2002ApJ...565..773T, 2001AJ....122..549V, 2012ApJ...752..162S,
  2014ApJ...794...75S} agree with Equation~(\ref{eqn:sed}), the
composite of \citet{2004ApJ...615..135S}, which uses more than 100
quasars at $z<0.1$, is somewhat steeper, with a EUV slope of $-0.56$.
The quasars considered by \citet{2004ApJ...615..135S} are fainter
($M_i(z=2)>-26$) than those considered by \citet{2015MNRAS.449.4204L},
which suggest that faint quasars may have a steeper EUV spectrum.  We
therefore assume an SED of the form
\begin{equation}
f_\nu\propto\begin{cases}
               \nu^{-0.61\pm 0.01} & \text{if}~\lambda\geq 912~\text{\AA},\\
               \nu^{-0.56\pm 0.61} & \text{if}~600~\text{\AA}<\lambda<912~\text{\AA}.\\                
               \end{cases}
\label{eqn:sed_faint}
\end{equation}
for AGN with $M_{1450}<-23$.

The rate of emission of photons of frequency $\nu$ by quasars can be
written as
\begin{equation}
\dot n_\nu = \int dM_\nu \phi(M_\nu) \frac{L_\nu(M_\nu)}{h\nu}.
\end{equation}
Here the integral is over a suitable range of magnitudes, the
monochromatic luminosity $L_\nu(M)$ is related to the (absolute AB)
magnitude by \citep{1983ApJ...266..713O}
\begin{equation}
M_\nu = -2.5\log_{10}L_\nu+51.60,
\end{equation}
and $\phi$ is the luminosity function from Equation~(\ref{eqn:dpl}).
The luminosity at 1~Ry is related to that at 1450~\AA\ by
Equation~(\ref{eqn:sed}) or (\ref{eqn:sed_faint})
\begin{equation}
  L_{912}=L_{1450}\left(\frac{\nu_{912}}{\nu_{1450}}\right)^{-0.61}=L_{1450}\left(\frac{912}{1450}\right)^{0.61},
\end{equation}
depending on the AGN luminosity.  The corresponding physical volume
emissivity is 
\begin{equation}
\epsilon_\nu = \dot n_\nu h\nu (1+z)^3.
\label{eqn:epsilon}
\end{equation}
The open and filled black circles with errorbars in
Figure~\ref{fig:e912_2} show the resultant 1~Ry emissivity when the
luminosity function is integrated down to $M_{1450}<-21$ (open
circles) and when it is integrated down to $M_{1450}<-18$ (filled
circles).  Redshift bins that were removed from analysis due to large
systematic errors are not shown.  Similar to the previous figures, the
black open circles in this figure show the result form individual
redshift bins, while the black curve shown the result from best-fit
global model.  Due to the problems with the global luminosity function
models discussed above, we avoid using them to describe the emissivity
evolution.  Instead, we describe the emissivity evolution by the
5-parameter functional form \citep{2012ApJ...746..125H}
\begin{equation}
  \epsilon_{912}=\epsilon_0(1+z)^a\frac{\exp(-bz)}{\exp(cz)+d}.
  \label{eqn:e912fit}
\end{equation}
We fit this to the points shown in Figure~\ref{fig:e912_2} assuming a
Gaussian likelihood in each bin.  The corresponding best-fit curves
and the corresponding one-sigma uncertainty is shown in red
($M_{1450}<-18$) and blue ($M_{1450}<-21$).  The best-fit form of
Equation~\ref{eqn:e912fit} is given by 
\begin{multline}
  \epsilon_{912}=(10^{24.49}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}})(1+z)^{7.57}\\\times\frac{\exp(-1.78z)}{\exp(1.01z)+29.20}
\end{multline}
for $M_{1450}<-18$, and by 
\begin{multline}
  \epsilon_{912}=(10^{24.11}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}})(1+z)^{6.64}\\\times\frac{\exp(-0.65z)}{\exp(1.82z)+20.45}
\end{multline}
for $M_{1450}<-21$.  The 1~Ry emissivity increases rapidly from $z=0$
up to $z=2$ and then stays roughly constant until up to $z=3.5$.  At
higher redshifts, due to the relatively steeper faint end slope of the
luminosity function, the integration limit makes a large difference in
the resultant emissivity.  For the conservative case, in which we
integrate under the luminosity function down to $M_{1450}=-20$, the
emissivity drops rapidly at $z>3.5$For comparison, various other
published determinations of the 1~Ry emissivity of quasars are also
shown in both panels of Figure~\ref{fig:e912_2}.  We now comment on the
comparison of our results with these measurements.
\citet{2009A&A...507..781S} combined data from the Hamburg/ESO survey
and the SDSS to measure a quasar luminosity function at $z=0$ in their
$B_J$ band to minimize host galaxy contribution.  We convert their
$B_J$ magnitudes (Vega system) to $M_{1450}$ (AB) as
\begin{equation}
  M_{1450,\mathrm{AB}}=M_{B_J, \mathrm{Vega}}+0.59.  
\end{equation}
In this magnitude system, the luminosity function reported by
\citet{2009A&A...507..781S} has a very faint break luminosity of
$M_*=-18.87$.  The faint-end slope is also steep ($\beta=-2$).  We
integrate this luminosity function down to our limiting magnitudes of
$M_{1450}=-18$ and $-21$.  The resultant values are shown by the open
and closed brown circles at $z=0$ in Figure~\ref{fig:e912_2}.  Our
emissivity values at $z=0$ lie in between the
\citet{2009A&A...507..781S} measurements.  The convergence in the
emissivity is slower in their measurements than in our models because
of the shallower faint-end slope at this redshift in our model
($\beta\sim -1.22$).  We discuss the 1~Ry emissivity and the
corresponding hydrogen photoionization rate at $z=0$ below.

The brown dashed curve in Figure~\ref{fig:e912_2} shows the AGN 1~Ry
emissivity model of \citet{2012ApJ...746..125H}, which based on the
bolometric luminosity function model of \citet{2007ApJ...654..731H}.
Their assumed emissivity agrees reasonably well with our
$M_{1450}<-21$ case.  The green dotten curve in Figure~\ref{fig:e912_2}
shows the model presented by \citet{2015ApJ...813L...8M}.  This model
disagrees with ours rather severely at almost all redshifts in the
range considered here.  Note that a direct comparison with
\citet{2012ApJ...746..125H} and \citet{2015ApJ...813L...8M} is
difficult because these models integrate the luminosity function to a
fixed fraction of the break luminosity $L_*$ instead of a fixed
absolute magnitude.  The chosen limite by \citet{2012ApJ...746..125H}
and \citet{2015ApJ...813L...8M} is $0.01L_*$.  Using a limit that
depends on the break luminosity can be problematic as different quasar
surveys used to develop these emissivity models often report
strikingly different break luminosity values.  Even when these samples
are homogeneized appropriately, have such an integration limit is only
justified if the faint-end slope of the luminosity function is
sufficiently shallow.

The grey dashed curve shows the emissivity model of
\citet{2017MNRAS.466.1160M}.  These authors integrate the luminosity
function down to $M_{1450}=-19$.  However, their model strongly
disagrees with our inference, potentially due to biases resulting from
combining binned luminosity function estimates from different sources
inhomogeneously.  The green curves in Figure~\ref{fig:e912_2} show the
luminosity function derived from a variability-selected sample
observed using the Sloan telescope and the Multiple Mirror Telescope
(MMT) by \citet{2013A&A...551A..29P}.  This sample of 1877 quasars
does not overlap with the variability-selected sample reported by the
BOSS survey \citep{2013ApJ...773...14R}.  \citet{2013A&A...551A..29P}
assum constant luminosity function slopes with a break at $z=2.2$ and
assume a pure luminosity evolution.  This leads to a discontinuity in
the emissivity evolution in their model at $z=2.2$.  We convert their
$g$-band magnitudes to $M_{1450}$ and integrate the resultant
luminosity function down to our two chosen integration limits.  The
result is shown in Figure~\ref{fig:e912_2} by the solid and dashed
orange curves, which correspond to $M_{1450}<-21$ and $-18$,
respectively.  For $M_{1450}<-21$, our models are in reasonable
agreement at $z<2.2$.  At other redshifts and for $M_{1450}<-21$, the
models disagree by 10--30\%.  Figure~\ref{fig:e912_2} also shows the
model presented by \citet{2016A&A...587A..41P}.  We consider their
PLE$+$LEDE model, in which the faint-end slope is assumed to stay
constant with redshift.  Although the emissivity evolution in this
model is continuous at $z=2.2$, it is not smooth.  This model agrees
with our $M_{1450}<-18$ result to a better degree relative to the
\citet{2013A&A...551A..29P} model.  We also compare our result with
the PLE$+$LEDE luminosity function model presented by
\citet{2017A&A...608A..64C} by reanalysing the
\citet{2016A&A...587A..41P} sample with an improved $K$-correction
implementation.  \citet{2017ApJ...847L..15O} recently fit a double
power law luminosity function model to a combined binned samples of
\citet{2016ApJ...833..222J}, \citet{2010AJ....139..906W}, and
\citet{2015ApJ...798...28K}, and an X-ray-selected AGN candidate with
photometric redshift $z\sim 6$ reported by
\citet{2018MNRAS.474.2904P}.  We show the resultant 1~Ry emissivity by
orange rectangle in Figure~\ref{fig:e912_2}.  The lower side of the
rectangle corresponds to the emissivity for the
\citet{2017ApJ...847L..15O} model excluding the
\citet{2018MNRAS.474.2904P} AGN.  When this AGN candidate is included,
the emissivity is higher; this is shown by the upper end of the
rectangle.  The open rectangle corresponds to $M_{1450}<-18$ and the
closed rectangle corresponds to $M_{1450}<-21$.

The red open cirles with error bars in Figure~\ref{fig:e912_2} show the
determination from the fits of \citet{2015AA...578A..83G}.  These
authors also choose a break luminosity-dependent integration limit of
$0.01L_*$, which corresponds to $M_{1450}\sim -18$ in their model.
The resultant emissivities are factors of 2 to 3 higher than our
determinations for $z=4$--$6$.  This is puzzling at first sight,
because the AGN candidates reported by \citet{2015AA...578A..83G} are
consistent with our luminosity function estimates obtained without
these candidates (see Appendix~\ref{sec:conv}).  Our luminosity
function are also somewhat steeper than those reported by
\citet{2015AA...578A..83G}.  The discrepancy is explained by the
difference in the two luminosity function models at intermediate
magnitudes.  We find that the data prefer a much brighter break
luminosity than that infered by \citet{2015AA...578A..83G}.  This
reduces our emissivities relative to their estimates.  We go into this
issue in further detail in Appendix~\ref{sec:conv}.

\citet{2018AJ....155..131M} recently extended their previous Stripe~82
AGN sample by 1.5 magnitude and fit a double power law luminosity
function model to a combined SDSS $+$ Stripe~82 $+$ CFHTLS sample at
$4.7 < z < 5.1$.  These authors fixed the bright-end slope to
$\alpha=-4$ and obtained a shallower faint-end slope ($\beta=-1.97$)
than our models at this redshift ($\beta\sim -2.3$).  Rescaling their
LF to our cosmology and assumed our SED obtain the emissivities shown
by the green circles in Figure~\ref{fig:e912_2}.  Again the open and
filled circles corresponds to our two integration limits.  Our
emissivity agrees with the measurement of \citet{2018AJ....155..131M}
for $M_{1450}<-21$ but is higher than their measurement for
$M_{1450}<-18$, which is not surprising due to the difference in the
luminosity function slopes.  The emissivity derived from the
luminosity function of \citet{2018PASJ...70S..34A} is shown in yellow
in Figure~\ref{fig:e912_2}.  These authors report 1668 AGN candidates at
$3.5<z<4.3$, of which 76 have spectroscopic redshifts.  Their reported
faint-end slope is very flat ($\beta=-1.3\pm 0.05$), inconsistent with
our determination at all redshifts.  Their inferred emissivity is
consistent with our estimate for $M_{1450}\sim -21$.  Their emissivity
does not change significantly with the integration limit thanks to the
shallow slope.  We also compare our emissivities with the
determinations reported by \citet{2012ApJ...755..169M} at $z\sim 3.2$
and $z\sim 4$.  Their emissivity in reasonably agreement with our
model for $M_{1450}<-21$ at $z\sim 3.2$.  But their $M_{1450}<-18$
emissivity disagrees with all other high-redshift estimates, possibly
indicating a systematic error.  Our emissivity estimates are in good
agreement with those of \citet{2018MNRAS.474.2904P}.  Mention
Bongiorno.

>>>>

\begin{figure*}
  \begin{center}
    \begin{tabular}{cc}
      \includegraphics[width=0.47\textwidth]{emissivity_18.pdf} & 
      \includegraphics[width=0.47\textwidth]{emissivity_21.pdf} \\
      % gammapi.py -- draw_emissivity()
    \end{tabular}
  \end{center}
  \caption{The 912~\AA\ emissivity of AGN assuming 100\% escape
    fraction down to a limiting magnitude for a luminosity function
    integration limit of $M_{1450}=-18$ (left panel) and
    $M_{1450}=-21$ (right panel).  Black filled circles with error
    bars in both panels show the emissivity determinations in redshift
    bin deemed to have low systematic errors.  Open circles show
    emissivities for redshift bins that we remove from analysis due to
    high systematic errors.  Solid red curves in both panels show the
    best fit emissivity evolution model, with the shaded area showing
    the one-sigma (68.26\%) uncertainty.  Also shown for comparison in
    both panels are models by \citet[pentagon
      symbol]{2009A&A...507..781S}, \citet[star]{2012ApJ...755..169M},
    \citet[square]{2015AA...578A..83G},
    \citet[triangle]{2018PASJ...70S..34A},
    \citet[circle]{2018AJ....155..131M},
    \citet[diamond]{2018MNRAS.474.2904P}, \citet[open
      rectangle]{2017ApJ...847L..15O}, \citet[dotted green
      curve]{2015ApJ...813L...8M}, \citet[dashed
      brown]{2012ApJ...746..125H}, \citet[dashed
      grey]{2017MNRAS.466.1160M}, \citet[dashed
      blue]{2013A&A...551A..29P}, \citet[solid
      cyan]{2016A&A...587A..41P}, and \citet[solid
      blue]{2017A&A...608A..64C}}
  \label{fig:e912_2}
\end{figure*}

@@

We now discuss the contribution of AGN to the hydrogen and helium
reionization in our luminosity function model.  We first derive the
expected evolution of the 912\,\AA\ emissivity of AGN in our model,
and then use this to estimate the \HI\ photoionization rate and the
average \HeIII\ fraction.

@@

We assume that all quasars have a universal UV SED, parameterised by
\citet{2015MNRAS.449.4204L} as a power law with a break at 912~{\AA},
\begin{equation}
f_\nu\propto\begin{cases}
               \nu^{-0.61\pm 0.01} & \text{if}~\lambda\geq 912~\text{\AA},\\
               \nu^{-1.70\pm 0.61} & \text{if}~600~\text{\AA}<\lambda<912~\text{\AA}.\\                
               \end{cases}
\label{eqn:sed}
\end{equation}
This fit was derived by \citet{2015MNRAS.449.4204L} from a composite
spectrum of 53 quasars at $z\sim 2.4$.  While four published composite
quasar UV SEDs \citep{2002ApJ...565..773T, 2001AJ....122..549V,
  2012ApJ...752..162S, 2014ApJ...794...75S} agree with
Equation~(\ref{eqn:sed}), the composite of
\citet{2004ApJ...615..135S}, which uses more than 100 quasars at
$z<0.1$, is somewhat steeper, with a EUV slope of $-0.56$.  The
quasars considered by \citet{2004ApJ...615..135S} are fainter
($M_i(z=2)>-26$) than those considered by \citet{2015MNRAS.449.4204L},
which suggest that faint quasars may have a steeper EUV spectrum.  We
therefore assume an SED of the form
\begin{equation}
f_\nu\propto\begin{cases}
               \nu^{-0.61\pm 0.01} & \text{if}~\lambda\geq 912~\text{\AA},\\
               \nu^{-0.56\pm 0.61} & \text{if}~600~\text{\AA}<\lambda<912~\text{\AA}.\\                
               \end{cases}
\label{eqn:sed_faint}
\end{equation}
for AGN with $M_{1450}<-23$.

The rate of emission of photons of frequency $\nu$ by quasars can be
written as
\begin{equation}
\dot n_\nu = \int dM_\nu \phi(M_\nu) \frac{L_\nu(M_\nu)}{h\nu},
\end{equation}
where the integral is over a suitable range of magnitudes, the
monochromatic luminosity $L_\nu(M)$ is related to the (absolute AB)
magnitude by \citep{1983ApJ...266..713O}
\begin{equation}
M_\nu = -2.5\log_{10}L_\nu+51.60,
\end{equation}
and $\phi$ is the luminosity function.  The 912\,\AA\ luminosity is
related to the UV luminosity at 1450\,\AA\ by Equation~(\ref{eqn:sed})
or (\ref{eqn:sed_faint})
\begin{equation}
  L_{912}=L_{1450}\left(\frac{\nu_{912}}{\nu_{1450}}\right)^{-0.61}=L_{1450}\left(\frac{912}{1450}\right)^{0.61},
\end{equation}
depending on the AGN luminosity.  The corresponding comoving volume
emissivity is
\begin{equation}
\epsilon_\nu = \dot n_\nu h\nu.
\label{eqn:epsilon}
\end{equation}
Figure~\ref{fig:e912_2} shows the comoving 912\,\AA\ emissivity when
the luminosity function is integrated down to $M_{1450}<-21$ (right
panel) and when it is integrated down to $M_{1450}<-18$ (left panel).
Redshift bins that were removed from analysis due to large systematic
errors are shown as open circles.  The emissivity peaks at $z=2$--$3$,
depending on the luminosity integration limit, at
$\epsilon_{912}=10^{25}\,\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}$
and decreased rapidly towards high redshifts.  A continuous
description of this emissivity evolution is valuable in deriving the
hydrogen photoionizing flux in the IGM.  In principle, the luminosity
function evolution models discussed in the previous section provide
such a description.  Unfortunately, as discussed above, all of these
models suffer from pathologies such as non-monotonic or divergent AGN
number densities, likely resulting from residual systematic errors in
the data.  Therefore, here we describe the emissivity evolution by the
five-parameter functional form used by \citet{2012ApJ...746..125H}
\begin{equation}
  \epsilon_{912}=\epsilon_0(1+z)^a\frac{\exp(-bz)}{\exp(cz)+d}.
  \label{eqn:e912fit}
\end{equation}
We fit this model to the emissivity estimates in the redshift bins,
shown in Figure~\ref{fig:e912_2}, assuming a Gaussian likelihood for
the emissivity in each bin.  The resultant best-fit curves and the
corresponding one-sigma uncertainties are shown in
Figure~\ref{fig:e912_2} for $M_{1450}<-18$ and $M_{1450}<-21$.  The
912\,\AA\ emissivities in various redshift bins and in these best-fit
models are tabulated in Appendix~\ref{sec:tables}.  The best-fit
form of Equation~\ref{eqn:e912fit} is given by
\begin{multline}
  \epsilon_{912}=(10^{24.49}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}})(1+z)^{7.57}\\\times\frac{\exp(-1.78z)}{\exp(1.01z)+29.20}
\end{multline}
for $M_{1450}<-18$, and by 
\begin{multline}
  \epsilon_{912}=(10^{24.11}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}})(1+z)^{6.64}\\\times\frac{\exp(-0.65z)}{\exp(1.82z)+20.45}
\end{multline}
for $M_{1450}<-21$.

Before proceeding to derive a hydrogen photoionization rate estimate
from these emissivities, we now comment on the comparison of our
results with estimates from the literature.  Several of these are
shown in Figure~\ref{fig:e912_2}.  The brown dashed curve in
Figure~\ref{fig:e912_2} shows the AGN 912\,\AA\ emissivity model of
\citet{2012ApJ...746..125H}, which is based on the bolometric
luminosity function model of \citet{2007ApJ...654..731H}.  Their
assumed emissivity agrees reasonably well with our $M_{1450}<-21$
case, although at its maximum the emissivity in the
\citet{2007ApJ...654..731H} model is lower by about 20\%.  The
differences between the two models are much larger for $M_{1450}<-18$.
Figure~\ref{fig:e912_2} also shows the model presented by
\citet{2015ApJ...813L...8M}.  This model disagrees with ours rather
severely at almost all redshifts in the range considered here, for
both of our integration limits.  It is important to note here that a
direct comparison of our model with \citet{2012ApJ...746..125H} and
\citet{2015ApJ...813L...8M} is difficult because these models
integrate the luminosity function to a fixed fraction of the break
luminosity $L_*$ instead of a fixed absolute magnitude.  The chosen
limite by \citet{2012ApJ...746..125H} and \citet{2015ApJ...813L...8M}
is $0.01L_*$.  Using a limit that depends on the break luminosity is
problematic as different quasar surveys used to develop these
emissivity models often report strikingly different break luminosity
values.  Even when these samples are homogeneized appropriately, have
such an integration limit is likely only justified if the faint-end
slope of the luminosity function is sufficiently shallow.  This issue
also affects some other models in the literature, such as those
presented by \citet{2015AA...578A..83G}, \citet{2015MNRAS.451L..30K}
and \citet{2018arXiv180104931P}.

\citet{2017MNRAS.466.1160M} integrated the luminosity function down to
$M_{1450}=-19$.  However, their model strongly disagrees with our
inference, as seen in Figure~\ref{fig:e912_2}, potentially due to
biases resulting from inhomogeneously combining binned luminosity
function estimates from different data sets.  The emissivity
determinations from the luminosity function derived from a
variability-selected sample observed using the Sloan telescope and the
Multiple Mirror Telescope (MMT) by \citet{2013A&A...551A..29P} is in
agreement with our $M_{1450}<-21$ determination for $z<2.2$.  At other
redshifts and for $M_{1450}<-18$, the models disagree by 10--30\%.
The sample of 1877 quasars presented by \citet{2013A&A...551A..29P} is
not included in our analysis, and therefore provides a cross-check.
(This sample also does not overlap with the variability-selected
sample reported by the BOSS survey \citep{2013ApJ...773...14R}.)
\citet{2013A&A...551A..29P} assume constant double power law
luminosity function slopes with a break at $z=2.2$ and assume a pure
luminosity evolution.  This leads to a discontinuity in the emissivity
evolution in their model at $z=2.2$.  In Figure~\ref{fig:e912_2}, we
convert their $g$-band magnitudes to $M_{1450}$ and integrate the
resultant luminosity function down to our two chosen integration
limits with our chosen SED for a direct comparison.
Figure~\ref{fig:e912_2} also shows the model presented by
\citet{2016A&A...587A..41P}.  We consider their PLE$+$LEDE model, in
which the faint-end slope is assumed to stay constant with redshift.
Although the emissivity evolution in this model is continuous at
$z=2.2$, unlike in the \citet{2013A&A...551A..29P} model, it is not
smooth.  This model agrees with our $M_{1450}<-18$ result to a better
degree relative to the \citet{2013A&A...551A..29P} model, bjt it
results in a higher emissivity in the $M_{1450}<-21$ case.
\citet{2017A&A...608A..64C} reanalysed the \citet{2016A&A...587A..41P}
sample with an improved $K$-correction implementation, but, as seen in
Figure~\ref{fig:e912_2}, their estimate is higher by 50\% or more
throughout the redshift range of their data.

At higher redshifts, \citet{2017ApJ...847L..15O} recently fit a double
power law luminosity function model to a combined binned samples of
\citet{2016ApJ...833..222J}, \citet{2010AJ....139..906W}, and
\citet{2015ApJ...798...28K}, and an X-ray-selected AGN candidate with
photometric redshift $z\sim 6$ reported by
\citet{2018MNRAS.474.2904P}.  We show the resultant
912\,\AA\ emissivity by a rectangle in Figure~\ref{fig:e912_2}.  The
lower side of the rectangle corresponds to the emissivity for the
\citet{2017ApJ...847L..15O} model excluding the
\citet{2018MNRAS.474.2904P} AGN.  When this AGN candidate is included,
the emissivity is higher; this is shown by the upper end of the
rectangle.  Our emissivities broadly in agreement with the
determination of \citet{2017ApJ...847L..15O}.  Figure~\ref{fig:e912_2}
shows the determination from the fits of \citet{2015AA...578A..83G}.
These authors also choose a break luminosity-dependent integration
limit of $0.01L_*$, which corresponds to $M_{1450}\sim -18$ in their
model.  The resultant emissivities are factors of 2 to 3 higher than
our determinations for $z=4$--$6$ for $M_{1450}<-21$.  This is
puzzling at first sight, because the AGN candidates reported by
\citet{2015AA...578A..83G} are consistent with our luminosity function
estimates obtained without these candidates (see
Appendix~\ref{sec:conv}).  Our luminosity function are also somewhat
steeper than those reported by \citet{2015AA...578A..83G}.  The
discrepancy is explained by the difference in the two luminosity
function models at intermediate magnitudes.  We find that the data
prefer a much brighter break luminosity than that inferred by
\citet{2015AA...578A..83G}.  This reduces our emissivities relative to
their estimates.  We go into this issue in further detail in
Appendix~\ref{sec:conv}.

\citet{2018AJ....155..131M} recently extended their previous Stripe~82
AGN sample by 1.5 magnitude and fit a double power law luminosity
function model to a combined SDSS $+$ Stripe~82 $+$ CFHTLS sample at
$4.7 < z < 5.1$.  These authors fixed the bright-end slope to
$\alpha=-4$ and obtained a shallower faint-end slope ($\beta=-1.97$)
than our models at this redshift ($\beta\sim -2.3$).  Rescaling their
LF to our cosmology and assuming our SED result in the emissivities
shown in Figure~\ref{fig:e912_2}.  Our emissivity agrees with the
measurement of \citet{2018AJ....155..131M} for $M_{1450}<-21$ but is
higher than their measurement for $M_{1450}<-18$, which is not
surprising due to the difference in the luminosity function slopes.
The emissivity derived from the luminosity function of
\citet{2018PASJ...70S..34A} is also shown in Figure~\ref{fig:e912_2}.
These authors report 1668 AGN candidates at $3.5<z<4.3$, of which 76
have spectroscopic redshifts.  Their reported faint-end slope is very
flat ($\beta=-1.3\pm 0.05$), inconsistent with our determination at
all redshifts.  Their inferred emissivity is consistent with our
estimate for $M_{1450}< -21$.  Their emissivity does not change
significantly with the integration limit due to the shallow faint-end
slope.  As a result, our $M_{1450}< -18$ determination of the
emissivity is considerably higher than their estimate.  We also
compare our emissivities with the determinations reported by
\citet{2012ApJ...755..169M} at $z\sim 3.2$ and $z\sim 4$.  Their
emissivity in reasonable agreement with our model for $M_{1450}<-21$
at $z\sim 3.2$.  Our emissivity estimates are in good agreement with
recent estimates of \citet{2018MNRAS.474.2904P} at $z=4$--$5$.

At low redshifts, \citet{2009A&A...507..781S} combined data from the
Hamburg/ESO survey and the SDSS to measure a quasar luminosity
function at $z=0$ in their $B_J$ band to minimize host galaxy
contribution.  We convert their $B_J$ magnitudes (Vega system) to
$M_{1450}$ (AB) as
\begin{equation}
  M_{1450,\mathrm{AB}}=M_{B_J, \mathrm{Vega}}+0.59.  
\end{equation}
In this magnitude system, the luminosity function reported by
\citet{2009A&A...507..781S} has a very faint break luminosity of
$M_*=-18.87$.  The faint-end slope is also steep ($\beta=-2$).  We
integrate this luminosity function down to our limiting magnitudes of
$M_{1450}=-18$ and $-21$.  The resultant values are shown in
Figure~\ref{fig:e912_2}.  Our emissivity values at $z=0$ lie in
between the \citet{2009A&A...507..781S} measurements.  The convergence
in the emissivity is slower in their measurements than in our models
because of the shallower faint-end slope at this redshift in our model
($\beta\sim -1.22$).
